Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Final Changes to Simulation Section.

The column ``CI Coverage'' lists the experimental coverage of each interval.  In 
Panel A, all the intervals from two robust estimators are reasonably close to 
their nominal coverage, although they slightly under cover the true treatment effect.
Our proposed bootstrap procedure consistently performs well, as it is about a percentage point 
closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
analytical interval has coverage as bad as 31\% (in the second DGP) and never
higher than 86\%. In Panel B, the coverage does not change too much from Panel
A. It slightly increases in DGP 1 and decreases in DGP 2 and 3 for all three procedures. In presence of heteroskedasticity, the two robust procedures again perform
similarly and have coverage close to the nominal level. The final column, ``CI
Length,'' indicates that intervals from the two robust procedures have average lengths close to each other, while interval from the naive procedure has much
shorter length on average. Not surprisingly, the average length of intervals
from all three procedures increases when the data is heteroskedastic.

These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and similarly well compared to the analytical bias correction procedures proposed
by CCT.

>>>>

The column ``CI Coverage'' lists the experimental coverage of each procedure.  In 
Panel A, all the intervals produced by the two robust estimators are reasonably close to 
their nominal coverage, although they slightly under cover the true treatment effect.
Our proposed bootstrap procedure consistently performs well, as it is about a percentage point 
closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
analytical interval has coverage as low as 31\% (in the second DGP) and never
higher than 86\%.

Panel B presents results for the heteroskedastic case. The coverages obtained are similar to those in Panel A and highlight 
the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
similarly and have coverage close to the nominal level. The final column, ``CI Length,'' indicates that intervals from the
 two robust procedures have average lengths close to each other, while interval from the naive procedure has much shorter length on average.

These are DGPs where the naive confidence intervals are known to perform poorly, 
and this set of simulation results indicates that our proposed bootstrap approach is 
quite competitive with analytical methods for producing robust intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs
and performs similarly well compared to the analytical bias correction procedures proposed by CCT.
